---
title: "Analysis of Toronto Marriage License Statistics"
author: 
  - Ziheng Zhong
thanks: "Code and data are available at: https://github.com/iJustinn/Demonstration_Exercise."
date: today
date-format: long
abstract: |
  This document presents an analysis of marriage license statistics in Toronto.
  The analysis includes a time series graph of marriage licenses issued over time, grouped by civic center.
format: pdf
number-sections: true
bibliography: references.bib
---



```{r}
#| include: false
#| warning: false
#| message: false

library(here)
library(readr)
library(dplyr)
library(ggplot2)
library(tidyverse)
library(palmerpenguins)

getwd()

# Read the cleaned dataset
cleaned_data <- read.csv(here("data", "analysis_data", "analysis_data.csv"))
```



# Introduction

This document analyzes marriage licenses issued at various civic centers over a specified time period. We use @citeR and data provided by the Open Data Toronto portal (@citeODT) for this analysis.

The remainder of this paper is structured as follows. Data (@sec-data)....



# Data {#sec-data}

All data are downloaded directly from Open Data Toronto (@citeODT).

```{r}
#| label: fig-one
#| fig-cap: Toronto Marriage License Statistics
#| warning: false
#| echo: false
# Ensure that the DATE column is in proper date format
cleaned_data$DATE <- as.Date(cleaned_data$DATE)

# Plot the marriage licenses over time, grouped by civic center
ggplot(cleaned_data, aes(x = DATE, y = MARRIAGE_LICENSES, color = CIVIC_CENTRE)) +
  geom_line() + 
  labs(
    title = "Marriage Licenses Issued Over Time by Civic Centre",
    x = "Date",
    y = "Number of Marriage Licenses",
    color = "Civic Centre"
  ) +
  theme_minimal() +
  theme(
    legend.position = "right",
    plot.title = element_text(hjust = 0.5),
    panel.grid.major = element_line(size = 0.2, color = "gray")
  )
```
@fig-one we created shows the number of marriage licenses issued over time, broken down by different civic centers. Each line on the graph represents a specific civic center (e.g., ET, NY, SC), with the x-axis showing the date (from 2011 onwards) and the y-axis displaying the number of marriage licenses issued.

From the chart, we can observe how the trend of marriage licenses fluctuates over time for each center. Some civic centers, like TO, appear to issue more licenses compared to others, suggesting differences in population or demand for marriage services across regions. The chart also highlights potential seasonal trends or patterns, such as possible increases in marriage licenses during certain months.



\newpage


# References


